---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(lubridate)
library(tidyverse)
library(tsibble)
library(tsibbledata)
library(feasts)

date1 <- ymd_hms("2017-04-22 22:01:18")
date2 <- ymd_hms("2001-11-07 10:09:56")
```

```{r}
library(nycflights13)
```

Homework: Dates and Times
Question 1
Extract the different components (year, month, mday, yday, wday) from the variable date1. Add the labels to the month and do not abbreviate the month labels.
```{r}
date1
```

```{r}
year(date1)
```
```{r}
month(date1, label = TRUE, abbr = FALSE)
```
```{r}
mday(date1)
```
```{r}
yday(date1)
```
```{r}
wday(date1)
```

Question 2

Add 14 days to your date1 variable and store it in a variable called next_fortnight. Take away 10 years from your date2 variable, and store it in previous_decade.
```{r}
date1
```


```{r}
next_fortnight <- date1 + ddays(14)
```
```{r}
date2
```
```{r}
previous_decade <- date2 - years(10)
```

Question 3

Create a variable called this_year which contains today’s date. Then create an interval object which uses this_year and the previous_decade variable you made above. Store it in interval_years. Hint: you’ll need to use lubridate::interval in order to get the right function, as tsibble has one too

```{r}
this_year <- today()
interval_years <- lubridate::interval(this_year, previous_decade)
```
```{r}
this_year <- now()
interval_years <- lubridate::interval(this_year, previous_decade)
```
Question 4

Change the time zone of both your date variables to “America/New_York”, and call them nyc_date1 and nyc_date2.
```{r}
nyc_date1 <- ymd_hms(date1, tz = "America/New_York")
```

```{r}
nyc_date2 <- ymd_hms(date2, tz = "America/New_York")
```
Question 5

Use the flights data from the nycflights13 dataset. Make a date-time column called departure_date from the year, month, day, hour, and minute variables in the flights tibble.

```{r}
data(nycflights13)
```
```{r}
nycflights13::flights
```
```{r}
nycflights13::flights %>%
  mutate(departure_date = make_datetime(year, month, day, hour, minute))
```

Time series familiarity

Question 6

Start with the weather data from the nycflights13 package. Select all the variables related to temperature, humidity, and precipitation, and pick out the key and index variables. Have a look at your data, and write a small description of the time series you observe.

```{r}
nycflights13::weather
```
```{r}
weather_6 <- nycflights13::weather %>% 
  select(origin, time_hour, temp, humid, precip)
```


```{r}
ggplot(weather_6) + 
  geom_line(aes(x = time_hour, y = temp), colour = "purple")
```
```{r}
weather_day <- weather_6 %>%
  index_by(date = ~ day(., label = F)) %>%
  summarise(temp_mean = mean(temp, na.rm = TRUE))


ggplot(data = weather_day, aes(x = time_hour, y = temp_mean)) +
  geom_point() + 
  geom_line(group = 1)
```

```{r}
ggplot(weather_6) + 
  geom_line(aes(x = time_hour, y = humid), colour = "purple")
```


