---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(ggfortify)
```


```{r}
project <- read_csv("project_management.csv")
```
```{r}
project <- as.tibble(project)
```

```{r}
project %>% 
  ggplot()+
  aes(x = estimated_length, y = actual_length)+
  geom_point()
plot(project$estimated_length, project$actual_length)+
  text(project$estimated_length, project$actual_length, labels = seq(nrow(project)), cex = 0.7, pos = 2)
```
I think the data in the row 5, 29 and 18 are outliers. The data in row 5 is influential due to its leverage. 

```{r}
model <- lm(formula = actual_length ~ estimated_length, data = project)
model
```

```{r}
project <- project %>%
  add_predictions(model) %>%
  add_residuals(model)
```

```{r}
project %>%
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_line(aes(y = pred), col = "red")
```

```{r}
autoplot(model)
```
Number 5 is influential due to its leverage. 

```{r}
project_2 <- project %>% 
  filter(X1 != 18)
```

```{r}
model_2 <- lm(formula = actual_length ~ estimated_length, data = project_2)
model_2
```
Intercept is 0.175 days bigger. The coefficient is just 0.001 smaller. I don't think it is a great difference, so it would support classifying the omitted point as non-influential. 

```{r}
project_2 <- project_2 %>%
  add_predictions(model_2) %>%
  add_residuals(model_2)
```

```{r}
project_2 %>% 
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_line(aes(y = pred), col = "red")+
  geom_line(data = project, aes(y = pred), col = "black")
```
The lines are almost one over each other. This confirms that the outlier removed was non-influential. 

```{r}
project_3 <- project %>% 
  filter(X1 != 5)
```

```{r}
model_3 <- lm(formula = actual_length ~ estimated_length, data = project_3)
model_3
```
Intercept is 2.965 days bigger and the coefficient 0.212 smaller. This supports classifying the omitted point as an influential outlier. 

```{r}
project_3 <- project_3 %>%
  add_predictions(model_3) %>%
  add_residuals(model_3)
```

```{r}
project_3 %>% 
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_line(aes(y = pred), col = "red")+
  geom_line(data = project, aes(y = pred), col = "black")
```
The lines differ enough to state that the outlier removed was influential. 

```{r}
autoplot(model)
```
Residuals are fairly independent from each other as the line is almost horizontal and is near 0. 
Removing the outliers in lines 5 and 16, the residuals would be almost completely normally distributed.
The blue line wobbles round 0.8, so the residuals show no big systematic increase or decrease in variation across the range of data. This variation is a bit modified by the outlier in line 5. 
