---
title: "R Notebook"
output: html_notebook
---
1.1
```{r}
library(tidyverse)
library(infer)
```
```{r}
data("msleep")
```
```{r}
msleep
```

H0: Jabberwockies_sleep_total - μ sleep total = 0
Ha: Jabberwockies_sleep_total - μ sleep total != 0
Critical value = 0.05

```{r}
msleep <- msleep %>% 
filter(!is.na(sleep_total))
```
```{r}
msleep %>%
  ggplot(aes(x = sleep_total)) +
  geom_histogram(col = "white")
```
```{r}
msleep %>%
  ggplot(aes(y = sleep_total)) +
  geom_boxplot() +
  coord_flip()
```
```{r}
observed_stat <- msleep %>%
  summarise(mean_sleep_total = mean(sleep_total))
observed_stat
```

The observed stat in the sample is 10.4. It is bigger than 7. Let's check if the reason for that difference is sampling variation or it is a statistically significant difference.

```{r}
null_distribution <- msleep %>%
  specify(response = sleep_total) %>%
  hypothesize(null = "point", mu = 7) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
```
```{r}
null_distribution %>%
  visualise(bins = 30) + 
  shade_p_value(obs_stat = observed_stat$mean_sleep_total, direction = "both")
```

```{r}
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat$mean_sleep_total, direction = "both")
p_value
```
Here the p-value is 0, and so we reject H0 in favour of Ha. The mean of hours slept by the animals in the population is significatly different from the 7 hours slept by Jabberwockies as an average. 

--------------

H0: Omnivores_sleep_total - hervivores_sleep_total <= 0
Ha: Omnivores_sleep_total - hervivores_sleep_total > 0

```{r}
msleep %>%
  filter(vore %in% c("omni", "herbi")) %>% 
  ggplot(aes(y = sleep_total, x = vore)) +
  geom_boxplot()
```
The hours slept by the omnivores are much more centralised than that of herbivores. 
```{r}
msleep <- msleep %>% 
  filter(vore %in% c("omni", "herbi"))
```
```{r}
msleep %>%
  group_by(vore) %>%
  summarise(n = n())
```

```{r}
null_distribution <- msleep %>% 
  specify(sleep_total ~ vore) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi")) 

null_distribution
```
```{r}
observed_stat <- msleep %>% 
  specify(sleep_total ~ vore) %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))
  
observed_stat
```
```{r}
null_distribution %>%
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "right")
```

```{r}
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "right")

p_value
```
The p-value is bigger than 0.05, so we fail to reject H0: there is no significant evidence that omnivores sleep longer than herbivores.
