---
title: "R Notebook"
output: html_notebook
---
```{r}
library(dplyr)
```

2 MVP
2.2 if statements and functions
2.2.1
```{r}
multiply_by15_add4 <- function(x){
  x * 15 + 4
}
```
2.2.2 
```{r}
concept_organizer <- function(x){
  if (x %in% c("goose", "duck", "pigeon")){
    return("bird")  #return, not print
  } else{
    return("not bird")
  }
}
```
2.2.3
```{r}
multiply_by_10 <- function(x = 1){
  if (class(x) == "numeric"){ 
    # numeric in quotation marks
    return(x * 10)  
  } else{
    return("Invalid input")
  }
}

```
2.3 ifelse(), recode() and case_when()
2.3.1
```{r}
sizes <- c(13, 15, 10, 8, 22)
```

a) ifelse. The best for this exercise. It allow you to achive the result with less effort. 
```{r}
ifelse(sizes > 10, "Big", "Small")
```
b) recode. The worst one, it is needed to write every single number and equal them to "Big" or "Small" separately. 
```{r}
logical_big_sizes <- sizes > 10
factor_big_sizes <- as.factor(logical_big_sizes)
as.vector(recode(factor_big_sizes, "TRUE" = "Big", .default = "Small"))
# I did it this way to avoid writing each number to replace. 
```
c) case_when. Not as easy to write as the ifelse but good. 
```{r}
case_when(
  sizes > 10 ~ "Big", 
  T ~ "Small"
)
```
2.3.2 
```{r}
fruit <- c(
  "apple", 
  "apple", 
  "banana", 
  "cherry", 
  "cherry")
```

a) ifelse. The worst one. Not easy to apply. 
```{r}
ifelse(
  fruit == "apple", 
  "alpaca", 
  ifelse(
    fruit == "banana", 
    "bonobo", 
    ifelse(
      fruit == "cherry", 
      "chipmunk", 
      fruit)))
```
b) recode. The best one. 
```{r}
recode(
  fruit, 
  "apple" = "alpaca", 
  "banana" = "bonobo", 
  "cherry" = "chipmunk")
```
c) case_when
```{r}
case_when(
  fruit == "apple" ~ "alpaca", 
  fruit == "banana" ~ "bonobo", 
  fruit == "cherry" ~ "chipmunk"
)
```
2.3.3
```{r}
wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)
```
a) ifelse. Good one. It allows to apply less than, greater than and equal to. 
```{r}
ifelse(wife_age > husband_age, "Wife older", ifelse(wife_age < husband_age, "Husband older", "Same age"))
```
b) recode. Bad one, it is needed to select every possible value. 
```{r}
age_difference <- wife_age - husband_age #Better use the function sign to wrap the difference.
age_difference
recode(age_difference, "-5" = "Husband older", "-7" = "Husband older", "0" = "Same age", "1" = "Wife older", "4" = "Wife older")
```
c) case_when. Good one. It allows to apply less than, greater than and equal to. 
```{r}
case_when(
  wife_age > husband_age ~ "Wife older", 
  wife_age < husband_age ~ "Husband older", 
  T ~ "Same age"
)
```
2.4 Loops
```{r}
my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)
```
2.4.1
```{r}
for (item in my_list){
  if(class(item) == "character"){
    print(item)
  }
}
```
2.4.2
```{r}
i = 1
while(i <= length(my_list)){
  if(class(my_list[[i]]) == "character"){
    print(my_list[i])
  }
  i <- i + 1
}
```
2.4.3
```{r}
i = 1
while(i <= length(my_list)){
  if(length(my_list[[i]]) > 1){
    #for(item in my_list[[i]]){
      print(paste0(my_list[[i]], collapse = ""))
    #}
  }
  i <- i + 1
}
```

