---
title: "Cake ingredients"
date: "20/03/2020"
output: 
  html_document:
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,  include = FALSE}
library(tidyverse)
library(here)
```
<div class = "index">
  <ul> 
    <li>Creating the project and folders according to the structure:</li>
      <ul>
        <li>raw_data</li>
        <li>data_cleaning_scripts</li>
        <li>clean_data</li>
        <li>documentation_and_analyisis</li>
      </ul>
    <li>Coping the raw data into the folder raw_data. This data comes in two files:</li>
      <ul>
        <li>cake-ingredients-1961.csv.</li>
        <li>cake_ingredient_code.csv.</li>
      </ul>  
    <li>Creating two R Scripts inside data_cleaning scripts.</li>
      <ul>
        <li>First script to clean the data cake_ingredient_code.csv.</li>
        <li>Second script to clean the data cake-ingredients-1961.csv.</li>
        They inherit their names from the files containing the data they are cleaning, but both with underscores.
      </ul>
    <li>Following this structure in data_cleaning_script_code.R:</li>
  </ul>
</div>

##### packages and libraries --------------------------------------------------

install.packages("snakecase") <br /><br />
library(tidyverse) <br /><br />
library(janitor) <br /><br />
library(snakecase)


##### data reading ------------------------------------------------------------

cake_raw_data_code <- read_csv("raw_data/cake_ingredient_code.csv")

```{r}
cake_raw_data_code_presentation <- read_csv(here("raw_data/cake_ingredient_code.csv"))
cake_raw_data_code_presentation
```


##### data cleaning -----------------------------------------------------------

cake_raw_data_code <- cake_raw_data_code %>% <br /><br />
  &nbsp;&nbsp;&nbsp; mutate(ingredient = str_to_lower(ingredient)) %>% <br /><br />
  &nbsp;&nbsp;&nbsp; mutate(code = str_to_lower(code)) %>% <br /><br />
  &nbsp;&nbsp;&nbsp; mutate(ingredient = str_replace_all(ingredient, "\\s", "_")) %>% <br /><br />
  &nbsp;&nbsp;&nbsp; mutate(ingredient = str_replace(ingredient, "_cup", "") ) %>% <br /><br />
  &nbsp;&nbsp;&nbsp; mutate(measure = ifelse(is.na(measure) == T, "cup", measure))

<br /><br /><br /><br />
<div class = "index">
<li>Following this structure in data_cleaning_script_1961:</li>
</div>
<br /><br />

##### packages and libraries --------------------------------------------------

library(tidyverse) <br /><br />
ibrary(janitor) <br /><br />
library(outliers)


##### data reading ------------------------------------------------------------

cake_raw_data_1961 <- read_csv("raw_data/cake-ingredients-1961.csv")

```{r}
cake_raw_data_1961_presentation <- read_csv(here("raw_data/cake-ingredients-1961.csv"))
cake_raw_data_1961_presentation
```


##### data cleaning -----------------------------------------------------------

cake_raw_data_1961 <- cake_raw_data_1961 %>% <br /><br />
  &nbsp;&nbsp;&nbsp;clean_names() %>% <br /><br />
  &nbsp;&nbsp;&nbsp; mutate(cake = str_to_lower(cake)) %>% <br /><br />
  &nbsp;&nbsp;&nbsp; mutate(cake = str_replace_all(cake, "\\s", "_")) %>% <br /><br />
  &nbsp;&nbsp;&nbsp; pivot_longer(-cake, <br /><br />
               &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; names_to = "code", <br /><br />
               &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; values_to = "amount") 

cake_raw_data_1961 <- 
  &nbsp;&nbsp;&nbsp; left_join(cake_raw_data_1961, cake_raw_data_code, "code") %>% <br /><br />
  &nbsp;&nbsp;&nbsp; select(-code) %>% <br /><br />
  &nbsp;&nbsp;&nbsp; drop_na() %>% <br /><br />
  &nbsp;&nbsp;&nbsp; select(1, ingredient,measure, amount)
  
<br /><br />
I am pretty sure that the NAs correspond to ingredients with amount == 0.
We can't imput values to them as that would add new ingredients to the cakes. 
The best option is to drop them. <br /><br />
If we set -3 < zscores to < 3 we have three outliers in amounts.
But they are proportional to the other amounts, so we must keep them.

```{r}
cake_clean_data_1961 <- read_csv(here("clean_data/cake_clean_data_1961.csv"))
cake_clean_data_1961
```

##### data writing ------------------------------------------------------------

write_csv(cake_clean_data_1961, "clean_data/cake_clean_data_1961.csv")

<div class = "index">
<br /><br />
<li>Reading the csv into the analysis file and answer the questions.</li>
</div>
<br /><br />
<br /><br />

```{r, include}
cake_clean_data_1961 <- read_csv(here("clean_data/cake_clean_data_1961.csv"))
cake_clean_data_1961
```
<br /><br />

**Which cake has the most cocoa in it?**
```{r}
cake_clean_data_1961 %>% 
  filter(ingredient == "cocoa", amount == max(amount)) %>% 
  select(cake, amount)
```
<br /><br />

**For sponge cake, how many cups of ingredients are used in total?**
```{r}
cake_clean_data_1961 %>% 
  filter(cake == "sponge", measure == "cup") %>% 
  summarise(total_cups = sum(amount))
```
<br /><br />

**How many ingredients are measured in teaspoons?**
```{r}
cake_clean_data_1961 %>% 
  filter(measure == "teaspoon") %>% 
  group_by(ingredient) %>%
  summarise() %>% 
  tally(name = "ingredients_measured_in_teaspoons")
```
<br /><br />

**Which cake has the most unique ingredients?**
```{r}
times_used_ingredients <- cake_clean_data_1961 %>% 
  group_by(ingredient) %>% 
  summarise(times_used = n())
left_join(cake_clean_data_1961, times_used_ingredients, "ingredient") %>% 
  group_by(cake) %>% 
  summarise(sum_times_used = sum(times_used)) %>% 
  filter(sum_times_used == min(sum_times_used))
```
<br /><br />

**Which ingredients are used only once?**
```{r}
cake_clean_data_1961 %>% 
  group_by(ingredient) %>% 
  summarise(times_used = n()) %>% 
  filter(times_used == 1)
```