---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(GGally)

library(tidyverse)
titanic_set <- read_csv('titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```

```{r}
titanic_clean <- titanic_set %>%
  filter(survived %in% c(0,1)) %>%
# Convert to factor level
    mutate(sex = as.factor(sex), 
           age_status = as.factor(if_else(age <= 16, "child", "adult")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")), 
           survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes")), 
           port_embarkation = as.factor(embarked)) %>%
  select(sex, age_status, class, port_embarkation, sib_sp, parch, survived_flag) %>%
  na.omit()
```

```{r}
titanic_clean %>%
  ggpairs()
```
The variable survived shows correlation with sex, age_status, class, port_embarkation and probably parch. 
The probability of surviving was bigger for women, childreen, first and second class and port_embarkation != S. 

```{r}
n_data <- nrow(titanic_clean)


test_index <- sample(1:n_data, size = n_data*0.25)


test  <- slice(titanic_clean, test_index)


train <- slice(titanic_clean, -test_index)
```
I have chosen 0.25 because we don't have much data. 

```{r}
test %>%
 janitor::tabyl(survived_flag)
```
```{r}
train %>%
 janitor::tabyl(survived_flag)
```

The results are almost equal. It is balanced. 

```{r}
titanic_fit <- rpart(survived_flag ~ ., 
                     data = train, 
                     method = 'class')

rpart.plot(titanic_fit, yesno = 2)
```

```{r}
rpart.rules(titanic_fit, cover = TRUE)
```
```{r}
library(modelr)

# add the predictions
titanic_test_pred <- test %>%
                 add_predictions(titanic_fit, type = 'class')
```
```{r}
rpart.predict(titanic_fit, newdata=test[1:4,], rules=TRUE)
```

The important variables are sex, class, port_embarkation, parch and age_status. 

People with the highest probability of surviving were not males and didn't travel in lower class. They had a 95% probability of surving. 
People with the lowest probability of surviving were males, travelling in lower or middle class, not adults and sib_sp >= 3. 
