---
title: "R Notebook"
output: html_notebook
---
packages and libraries
```{r}
library(readr)
```

1 MVP

1.1 Read in the state_income_data.csv file using the appropriate function.
```{r}
read_csv("data/state_income_data.csv")
```
1.2 How do you specify your own column names when using read_csv()?
```{r}
read_csv(
  "data/state_income_data.csv", 
  col_names = c(
    "Index", 
    "State", 
    "Year2002", 
    "Year2003",
    "Year2004",
    "Year2005",
    "Year2006",
    "Year2007",
    "Year2008",
    "Year2009",
    "Year2010",
    "Year2011",
    "Year2012",
    "Year2013",
    "Year2014",
    "Year2015"
    )
)
```
1.3 Read in the cars.csv file and use the col_types() function to ensure you load in:

X1 as character
mpg, cyl, disp, hp as double
vs as logical

```{r}
read_csv(
  "data/cars.csv", 
  col_types = cols(
    X1 = col_character(), 
    mpg = col_double(), 
    cyl = col_double(), 
    disp = col_double(), 
    hp = col_double(), 
    vs = col_logical()
    )
)
```
1.4 Read in the scotland.txt file using the appropriate function.
```{r}
read_delim("data/scotland.txt", delim = ";")
```
1.5 How do you read text into a one element character vector?
With read_file or read_lines. 

1.6 Read in the steam-200k-sample.csv file. Fix any problems you may encounter.
```{r}
read_csv(
  "data/steam-200k-sample.csv", 
  skip = 5, 
  col_names = c(
    "customer id", 
    "game name", 
    "what", 
    "value", 
    "bought online"
    )
)
```
1.7 Read in the historic_eu_payments.tsv file. 
```{r}
read_tsv("data/historic_eu_payments.tsv")
```
1.8 How do you read lines of text into a multi-element text vector?
Using read_lines()
1.9 Read in the africa_health_data.dta file using the appropriate method.
```{r}
library("haven")
read_dta("data/africa_health_data.dta")
```
1.10 Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt
```{r}
library(readr)
library(jsonlite)
raw_sample_json <- read_file(
  "http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
sample_json <- parse_json(raw_sample_json)
sample_json

```

2 EXTENSION

```{r}
library(readxl)
library(openxlsx)
read_excel("data/green_bindle_consulting.xlsx", sheet = 8)
```
```{r}
install.packages("gdata")
library(gdata)
```
```{r}
sheetCount("data/green_bindle_consulting.xlsx", verbose = FALSE, perl = "perl")
```

```{r}
vector_to_write <- c("a", "b")
#wb <- createWorkbook("data/green_bindle_consulting.xlsx"
for (i in 1:8){
write.xlsx(vector_to_write,
"data/green_bindle_consulting.xlsx", 
startRow = 10, 
sheet = i
)
}
```
```{r}
read_excel("data/green_bindle_consulting.xlsx", sheet = 2)
```
```{r}

```


