---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
drinks_content <- read_csv("starbucks_drinkMenu_expanded.csv")
```



```{r}
head(drinks_content, 5)
```
```{r}
tail(drinks_content, 5)
```
```{r}
drinks_content
```

```{r}
dim(drinks_content)
```

```{r}
names(drinks_content)
```

```{r}
summarise(drinks_content, mean_calories = mean(Calories), median(Calories), variance_calories = var(Calories))
```
```{r}
hist(drinks_content$Calories)
```
```{r}
boxplot(drinks_content$Calories)
```
It is not a normal distribution as the median and mean do not have the same value. They differ by almost 9 calories. The median is smaller than the mean because the distribution has more observations on its left part. It has a small interquartile because most of the observations are between aprox 120 and 260 calories. The range between two standards deviations is from 0 to about 450 calories. It has an outlier with 510 calories. 


```{r}
outlier <- boxplot(drinks_content$Calories, plot = FALSE)$out
outlier
```
```{r}
view(drinks_content)
```
I wouldn't remove the outlier as the distribution has some other values near the outlier. 
```{r}
small_table <- drinks_content %>%
select(Beverage_category, Beverage, Beverage_prep, Calories) %>%
filter(is.na(TRUE))
small_table
view(small_table)
```
No NAs. 
```{r}
small_table <- drinks_content %>%
select(Beverage_category, Beverage, Beverage_prep, Calories)

```
```{r}
filter(small_table, Beverage_category == "Classic Espresso Drinks")
```
```{r}
drink_calories <-
  small_table %>%
  mutate(calorie_diff = 135 - Calories)
drink_calories
```

```{r}
drinks_grouped <- 
  drinks_content %>%
  group_by(Beverage_prep)
```
```{r}
drinks_summary <- summarise(drinks_grouped, mean_cal = mean(Calories))
drinks_summary
```
```{r}
drinks_summary <- arrange(drinks_summary, desc(mean_cal))
drinks_summary
```
```{r}
drinks_summary <- drinks_content %>%
  select(Beverage_category, Beverage, Beverage_prep, Calories) %>%
filter(Beverage_category == "Classic Espresso Drinks") %>%
mutate(calorie_diff = 135 - Calories) %>%
group_by(Beverage_prep) %>%
summarise(mean_cal = mean(Calories)) %>%
arrange(desc(mean_cal))
drinks_summary
```

```{r}
least_calories <- drink_calories %>% 
  select(Beverage, Calories) %>%
  arrange(desc(Calories)) %>%
  mutate(ranking =(min_rank(Calories))) %>%
  filter(ranking ==1)
least_calories
```
```{r}
most_calories <- drink_calories %>% 
  select(Beverage, Calories) %>%
  mutate(ranking =(min_rank(Calories))) %>%
  arrange(desc(Calories)) %>%
  filter(ranking == 242)
most_calories
```
```{r}
drinks_grouped
```

```{r}
above_average_calories <- drinks_grouped %>% 
  filter(Calories > mean(Calories))
above_average_calories
```
```{r}
drinks_distribution <- drinks_grouped %>%
  select(Beverage, Beverage_prep, Calories) %>%
  mutate(distribution_score = cume_dist(Calories)) %>%
  filter(distribution_score > 0.75)
drinks_distribution
```

